Viscous Erosion in Porous Media

### 2018-03-27 docs/methods/erosion_methods.tex
NM

	We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process, with the same spatial resolution, $N_\iin = 1024$, as before. Notice the body obtains a similar profile as observed previously, but with fixed area. Importantly, more numerical accuracy is now available to quantify the terminal state. The inset in Fig.~\ref{fixed_intface}(a) zooms on the rear of the body to demonstrate that, due to our numerical regularization, what appears to be a corner is actually smooth on a fine scale. We show in Fig.~\ref{fixed_intface}(b) the stress distributions on the same interfaces. As observed previously, the stress becomes more evenly distributed as erosion reshapes the body. The slight rise in shear near the front/rear corners that was observed in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that this effect was due to loss of accuracy. Rather, the late-time stress distributions in Fig.~\ref{fixed_intface}(b) decrease monotonically to zero near the stagnation points.

@@

These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches a terminal state. In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corners. In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters ($\eps = \sigma = 20/1024, 10/1024,$ and 5/1024) so that we can assess how the numerical regularization influences shape. Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time. The initially circular geometry has an aspect ratio of unity, and, as erosion carves a more slender form, the aspect ratio increases monotonically. The three simulations are all very close to one another, demonstrating convergence as $\eps, \sigma \to 0$. In the most accurate simulation (i.e.~the least smoothing), the aspect ratio tends to a value of 2.7 in long time.

Next, we aim to measure the opening angle that develops at the front and rear of the body. Since these simulations are actually smooth on a fine scale, a true corner does not exist and we must instead estimate the apparent angle due to a small region of high curvature. To this end, we first fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region excluding the front/rear stagnation points ($\alpha = 0, 0.5$). We then extrapolate the polynomial to the stagnation points, which gives an estimate of the angle there. Although it is subject to some uncertainty (to be examined below), we have found this strategy to give robust angle measurements. In Fig.~\ref{fig:arangle}(b), we show the opening angle on the eroding body for the same three cases of smoothing parameters. The method gives an angle measurement of $180^{\circ}$ for the initially circular geometry, thus providing some confirmation. As time moves forward, erosion carves a sharper corner and the angle decreases monotonically. Here, the effect of the smoothing parameters is more visible, but we still see convergence as $\eps, \sigma \to 0$. In the most accurate simulation (black), the opening angle converges to a value of $102^{\circ}$, which agrees precisely with the analytical prediction from Section \ref{LimitingShape}.

>>>>

	We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process, with the same spatial resolution, $N_\iin = 1024$, as before. Notice the body obtains a similar profile as observed previously, but with fixed area. Importantly, more numerical accuracy is now available to quantify the terminal state. The inset in Fig.~\ref{fixed_intface}(a) zooms on the rear corner demonstrate that, due to our numerical regularization, the body is actually smooth on a fine scale. We show in Fig.~\ref{fixed_intface}(b) the stress distributions on the same interfaces. As observed previously, the stress becomes more evenly distributed as erosion reshapes the body. The slight rise in shear near the front/rear corners that was observed in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that this effect was due to loss of accuracy. Rather, the late-time stress distributions in Fig.~\ref{fixed_intface}(b) decrease monotonically to zero near the stagnation points.

@@

These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches a terminal state. In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corners. In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters ($\eps = \sigma$ taking the values 20/1024, 10/1024, and 5/1024) to assess how the numerical regularization influences shape. Figure~\ref{fig:arangle}(a) shows the aspect ratio as it varies in time. The initially circular geometry has an aspect ratio of unity, and, as erosion carves a more slender form, the aspect ratio increases monotonically. The three simulations are all very close to one another, demonstrating convergence as $\eps, \sigma \to 0$. In the simulation with these least smoothing ($\eps = \sigma = 5/1024$), the aspect ratio tends to a value of 2.7 in long time.

Next, we aim to measure the opening angle of the front/rear corner. Since these simulated bodies are actually smooth, though, we must have a procedure to estimate the apparent angle that results from the high (but finite) curvature at the stagnation points. To this end, we fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region excluding the stagnation points ($\alpha = 0$ and 0.5). We then extrapolate the polynomial to the stagnation points, which gives an estimate of the angle there. Although this procedure is subject to some uncertainty (to be examined below), we have found it to give robust angle measurements. In Fig.~\ref{fig:arangle}(b), we show the opening angle on the eroding body for the same three cases of smoothing parameters. The method gives an angle measurement of $180^{\circ}$ for the initially circular geometry, thus providing some confirmation. As time moves forward, erosion carves a sharper corner and the angle decreases monotonically. Here, the effect of the smoothing parameters is more visible, but we still see convergence as $\eps, \sigma \to 0$. In the most accurate simulation (black), the opening angle converges to a value of $102^{\circ}$, which agrees precisely with the analytical prediction from Section \ref{LimitingShape}.
